### 2022-03-12 manuscript.tex
discussion additions
abstract added and some pictures updated

\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

\lstset{language=R,
    basicstyle=\small\ttfamily,
    stringstyle=\color{DarkGreen},
    otherkeywords={0,1,2,3,4,5,6,7,8,9},
    morekeywords={TRUE,FALSE},
    deletekeywords={data,frame,length,as,character},
    keywordstyle=\color{blue},
    commentstyle=\color{DarkGreen},
}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

@@

@@

\begin{figure}[htbp]
\centerline{\includegraphics[scale=.4]{dens_comp.png}}
\caption{Figure this out later}
\label{fig}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[scale=.4]{cum_comp.png}}
\caption{Figure this out later}
\label{fig}
\end{figure}

@@

In this paper we have reviewed four representation types commonly used in
probabilistic 
forecasting including proper scoring, data storage and ensemble model 
construction for each type. We presented the discrete mixture distribution
representation and argue that in terms of model flexibility, storage and 
ensemble building it is
comparable to discretized bins and interval forecasts but also provides a 
forecast with a continuous nominal resolution. Thus we advocate its use in
future forecasting projects like those done by the CDC and COVID-19 Forecast 
Hub.

>>>>

\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
% \makeatletter
% \def\maxwidth{ %
%   \ifdim\Gin@nat@width>\linewidth
%     \linewidth
%   \else
%     \Gin@nat@width
%   \fi
% }
% \makeatother

@@

\lstset{language=R,
    basicstyle=\small\ttfamily,
    stringstyle=\color{DarkGreen},
    otherkeywords={0,1,2,3,4,5,6,7,8,9},
    morekeywords={TRUE,FALSE},
    deletekeywords={data,frame,length,as,character},
    keywordstyle=\color{blue},
    commentstyle=\color{DarkGreen},
}
\makeatletter
% \newenvironment{kframe}{%
%  \def\at@end@of@kframe{}%
%  \ifinner\ifhmode%
%   \def\at@end@of@kframe{\end{minipage}}%
%   \begin{minipage}{\columnwidth}%
%  \fi\fi%
%  \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
%  \colorbox{shadecolor}{##1}\hskip-\fboxsep
%      % There is no \\@totalrightmargin, so:
%      \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
%  \MakeFramed {\advance\hsize-\width
%    \@totalleftmargin\z@ \linewidth\hsize
%    \@setminipage}}%
%  {\par\unskip\endMakeFramed%
%  \at@end@of@kframe}
% \makeatother

% \definecolor{shadecolor}{rgb}{.97, .97, .97}
% \definecolor{messagecolor}{rgb}{0, 0, 0}
% \definecolor{warningcolor}{rgb}{1, 0, 1}
% \definecolor{errorcolor}{rgb}{1, 0, 0}
% \newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

@@

\section*{Abstract}

Collaboration among multiple teams has played a major role in probabilistic
forecasting of influenza outbreaks, the COVID-19 pandemic, other disease
outbreaks and problems in other fields. When collecting forecasts from 
individual teams, ensuring that each team's model represents forecast
uncertainty according to the same format allows for direct comparison of 
forecasts as well as methods of constructing multi-model ensemble forecasts.
This paper outlines several common probabilistic forecast formats including
probability density functions, samples, binned distributions and  quantile 
forecasts and compares
their usage within the context of collaborative projects. The discrete mixture
distribution forecast format is presented as an attractive alternative to the 
former formats due to the flexibility such a forecast may have in shape as well
as the relatively low loss of information due to limited computer storage.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[scale=.1]{dens_comp.png}}
\caption{Figure this out later}
\label{fig}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[scale=.1]{cum_comp.png}}
\caption{Figure this out later}
\label{fig}
\end{figure}

@@

In this paper we have reviewed four representation types commonly used in
probabilistic 
forecasting including proper scoring, data storage and ensemble model 
construction for each type. We presented the discrete mixture distribution
representation and we argue that its use in collaborative probabilistic 
forecasting is preferable to the other representations.
In terms of model flexibility, storage and 
ensemble building it is
comparable to discretized bins and interval forecasts but also provides a 
forecast with a continuous nominal resolution. Thus we advocate its use in
future forecasting projects like those done by the CDC and COVID-19 Forecast 
Hub.

For a number of reasons, the adoption of finite mixture distributions as the
submission format may face hurdles. A forecast hub, along with modelers, using a 
different representation may simply not want to break from tradition. The 
implementation of new scoring and ensemble construction methods may be a 
barrier. One aspect of ensemble construction which received little attention in 
this paper is the selection of weights for components of an ensemble where each
of the components is mixture distribution. Computing requirements could become a
concern in such a problem and further research on this may provide
ideas of best methods for weight selection.

Another area of recommended research is the use of joint distributions for 
forecasting. We have only considered here probabilistic forecasting of one 
event at a time. Number of new infections in one week at one specific location
for example. This forecast is presented as a marginal distribution for that 
specific target, time and location. A joint distribution for forecasting 
multiple targets, times or locations may sometime be desirable and may require
further consideration on how joint mixture distributions could be used as a 
format in collaboration.
